---
title: "Murillo_CIS635_Project"
author: "Cleyde Murillo Jr"
date: "4/17/2021"
output: html_document
---
```{r, message = FALSE}
library(tidyverse)
library(ggcorrplot)
library(reshape2)
library(gridExtra)
library(e1071)
library(rpart)
library(lattice)
library(caret)
library(rpart.plot)
library(ggfortify)
```

First we begin by merging the sources together, preceded by munging the data via outliers, missing values, and ambiguity.

```{r}
trainA <- read.csv('dataTrainA.txt', header = TRUE, sep = '\t')
trainB <- read.csv('dataTrainB.txt', header = TRUE, sep = '\t')
train <- merge(trainA, trainB, by = 'id')
train <- train[order(train$id), -13]

testA <- read.csv('dataTestA.txt', header = TRUE, sep = '\t')
testB <- read.csv('dataTestB.txt', header = TRUE, sep = '\t')
test <- merge(testA, testB, by = 'id')
test <- test[order(test$id), -13]

```

By summarizing the data we can point out the attributes with outliers and missing values. Take note on: temp, bySys, vo2, throat, headA, runny, nausea, & diarrhea.

```{r}
summary(train)
```

In this case, we will replace all NA values with the median of their columns, then remove the outliers in the data.

```{r, message = FALSE}
nas <- train[rowSums(is.na(train)) > 0,]
outliers <- subset(train, (train$temp < 90) | (train$temp > 106) | (train$bpSys < 90) | (train$bpSys > 150) | (train$vo2 < 10) | 
                          (train$vo2 > 70) | (train$throat < 80) | (train$throat > 120) | (train$headA > 9) | (train$bodyA > 9) | (train$nausea > 1))
#Replaces NAs with medians
train <- train %>% 
   mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))

#Remove observations with outliers
train <- anti_join(train, outliers)
```

In this part we want to get a feel for how each variable looks after cleaning. We will follow through with visualizations of distributions, correlations, and plots.

```{r, message = FALSE}
#Excluding ID
melt.train <- melt(train[,-1])

ggplot(melt.train, aes(x = value, fill = variable)) +
      stat_density(show.legend = FALSE) +
      facet_wrap(~variable, scales = 'free')
```

```{r}
r <- cor(train[,-1], use = 'complete.obs')
ggcorrplot(r, hc.order = TRUE, type = 'lower', lab = TRUE)
```

```{r}
p1 <- ggplot(train, aes(atRisk.x, temp, color = temp < 98.6)) +
  geom_point()
p2 <- ggplot(train, aes(atRisk.x, headA,  color = atRisk.x)) +
  geom_point()
p3 <- ggplot(train, aes(atRisk.x, vo2,  color = atRisk.x)) +
  geom_point()
p4 <- ggplot(train, aes(atRisk.x, bpSys,  color = atRisk.x)) +
  geom_point()

grid.arrange(p1, p2, p3, p4, ncol = 2,
             top = 'Highest Risk Correlations')
```
Classifiers: Decision Tree, SVM, Naive Bayes
(Selection - Decision Trees)
Calculations for Accuracy, Recall (Sensitivity), Precision (Pos Pred Value)

```{r}
#Naive Bayes
nb <- naiveBayes(atRisk.x ~., train)
pnb <- predict(nb, test[,-6])
nbx <- table(true = test$atRisk.x, predict = pnb)
confusionMatrix(nbx)

#Decision Trees

for(i in c(6:12)){
  train[,i] <- as.factor(train[,i])
  test[,i] <- as.factor(test[,i])
}

dt <- rpart(atRisk.x ~ . -id, data = train)
pred <- predict(dt, test, type = 'class')
dtx <- table(true = pred, predict = test$atRisk.x)
confusionMatrix(dtx)
rpart.plot(dt, extra = 104, nn = TRUE)
qt <- cbind(test,pred)

#Support Vector Machines
svmtrain <- train[c(2:5,7:12,6)]
svmtest <- test[c(2:5,7:12,6)]
for(i in c(1:10)){
  svmtrain[,i] <- as.numeric(svmtrain[,i])
  svmtest[,i] <- as.numeric(svmtest[,i])
}


svmfit <- svm(atRisk.x ~ ., data = svmtrain, kernel = 'polynomial', scale = TRUE)
predlin <- predict(svmfit, svmtest[,c(1:10)])
svx <- table(true = svmtest[,11], predict = predlin)
confusionMatrix(svx)
```

```{r, message = FALSE}
trainA <- read.csv('dataTrainA.txt', header = TRUE, sep = '\t')
trainB <- read.csv('dataTrainB.txt', header = TRUE, sep = '\t')
testA <- read.csv('dataTestA.txt', header = TRUE, sep = '\t')
testB <- read.csv('dataTestB.txt', header = TRUE, sep = '\t')

WeeklyAnalysis <- function(srcA, srcB, srcC, srcD){
  
library(tidyverse)
library(ggcorrplot)
library(reshape2)
library(gridExtra)
library(e1071)
library(rpart)
library(lattice)
library(caret)
library(rpart.plot)
library(ggfortify)
library(ggthemes)

  train <- merge(srcA, srcB, by = 'id')
  train <- train[order(train$id), -13]

  test <- merge(srcC, srcD, by = 'id')
  test <- test[order(test$id), -13]
  
  outliers <- subset(train, 
                    (train$temp < 90) | (train$temp > 106) | (train$bpSys < 90) | (train$bpSys > 150) | (train$vo2 < 10) | 
                    (train$vo2 > 70) | (train$throat < 80) | (train$throat > 120) | (train$headA > 9) | (train$bodyA > 9))
  
  #Replaces NAs with medians
  train <- train %>% 
   mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))

  #Remove outliers
  train <- anti_join(train, outliers)
  
  #Convert to Factors
  for(i in c(6:12)){
  train[,i] <- as.factor(train[,i])
  test[,i] <- as.factor(test[,i])
  }
  
  #Model + Tree Plot
  dt <- rpart(atRisk.x ~ . -id, data = train)
  pred <- predict(dt, test, type = 'class')
  dtx <- table(true = pred, predict = test$atRisk.x)
  confusionMatrix(dtx)
  qt <- cbind(test,pred)
  qt <- qt[,c(1:5,7:12,6,13)]
  
  qt <- qt %>%
    mutate(Status = if_else(atRisk.x == pred, 'Correct', 'Incorrect'))
    qt$Status <- as.factor(qt$Status)
    
  #Plots
  b1 <- ggplot(qt, aes(x = temp, y = headA, color = Status)) + 
    ggtitle('Predicted Virus Risk') +
    ylab('Head Ache Score') +
    xlab('Body Temperature') +
    geom_point() +
    scale_color_manual(values = c("#4699DD",'#C93232'))
    theme_economist()
  
  qtt <- confusionMatrix(pred, test$atRisk.x)
  ct <- qtt$table
  
  #Textfile, PNGs
  write.csv(qt, file = 'PredictedData.txt', col.names = TRUE, row.names = FALSE)
  
  png('Tree_Plot.png')
  rpart.plot(dt, extra = 104, nn = TRUE)
  ggsave('PredictedDataBarPlot.png', plot = b1)
  ggsave('FourFoldPlot_ConfusionMatrix.png', plot = fourfoldplot(ct, color = c("#CC6666", "#99CC99"),
             conf.level = 0, margin = 1, main = "Confusion Matrix"))
  dev.off()
  
}

WeeklyAnalysis(trainA, trainB, testA, testB)


```

```{r}
x <- rbind(train, test)
x <- x[order(x$id),-1]
km <- kmeans(x, 4)


for(i in c(1:11)){
  x[,i] <- as.numeric(x[,i])
}

autoplot(km, x, frame = TRUE)
km$size

x$cluster <- km$cluster

summary(x[x$cluster == 1, ])
summary(x[x$cluster == 2, ])
summary(x[x$cluster == 3, ])
summary(x[x$cluster == 4, ])

```